UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-08-03 main.tex
:pencil: Update introduction

>>>>

	% However, the advantage of this particular scheme is questionable because 1) it does not fully exploit backscatter pattern and signal characteristics; 2) it requires non-coherent encoding at the primary transmitter, and re-encoding, precoding, and subtraction at the receiver; 3) the primary and backscatter symbols are mixed by multiplication instead of superposition.
	However, the advantage of this particular scheme is questionable because 1) it does not fully exploit backscatter pattern and signal characteristics; 2) non-coherent primary encoding is required at the transmitter while re-encoding, precoding, and subtraction are required at the receiver; 3) the primary and backscatter symbols are mixed by multiplication instead of superposition.

	% This receiving scheme, as would be discussed later, may not fully
